The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
rm net types comments

### Network types and construction (defining layers for the multilayer network)
<!-- TODO: should use something like "using syntax from Kivela 2014..." or 
Following [@Kivela_2014]:
other info to maybe include: the multilayer network was not node-aligned since
not all individuals were on all layers
the temporal aspect is ordinal coupling and landcover aspect is categorical coupling

Individuals were subset to ensure they had data collected in both seasons
-->

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (forest, forage, and open) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019]. <!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

>>>>

### Network types and construction
We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (forest, forage, and open) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019]. 
<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->
